---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```


```{r}
books <- read_csv("data/books.csv")
glimpse(books)
summary(books)
# I had a quick look here, doesn't seem to have NA?
# from summary, some of the numerical cols like num_pages and text_reviews_count
# has a min of 0, I will treat them as NA
```

TASK 1: I want to find top 10 most highly rated books. 

```{r}
names(books)

highly_rated <- books %>% 
  select(title,average_rating) %>% 
  slice_max(average_rating, n= 10, with_ties = FALSE)
  
highly_rated

#the list of top ten most highly rated books look bit strange.
#a lot of textbooks? 

#I want to check for the top 1o how many ratings they got in total
#if it's less than the average amount of ratings then they will be
#kicked out of top 10
```

```{r}
new_top_10 <- books %>% 
  select(title, average_rating, ratings_count) %>% 
  filter(ratings_count >= median(ratings_count)) %>% 
  slice_max(average_rating, n = 10, with_ties = FALSE)

new_top_10

#This list looks a lot better. 
```



TASK 2: I want to have a look at publishers, 
see who published most amount of book 

```{r}
books_publisher <- books %>% 
  count(publisher)%>% 
  slice_max(n, n = 10, with_ties = FALSE)
books_publisher

#Vintage published 318 books 
#I used count here, I want to try group_by later.  
```



TASK 3: There's a lot of Harry Potter books. 
I will have a look and see which one is the best. 

```{r}
hp_books <- books %>% 
  select(title, authors, average_rating) %>% 
   filter(grepl('Harry Potter', title)) %>% 
  filter(grepl('J.K. Rowling', authors)) %>% 
  slice_max(average_rating, n = 3, with_ties = FALSE)

hp_books

#Top 2 are not individual books.
#So Harry Potter and the Half-Blood Prince is the best 4.57

```



TASK 4: Now I am going to have a look at authors, 
see who wrote the highest amount of books. 
I want to use group_by this time.

```{r}
authors_book <- books %>% 
   group_by(authors)%>%
  summarise(books_wrote = n()) %>% 
  slice_max(books_wrote, n = 10, with_ties = FALSE)
authors_book

#P.G. Wodehouse and Stephen King wrote 40 books, 
```



TASK 5: I am going to have a look at languages, I will count 
eng_US the smae as eng. I want to see which language published 
the highest amount of books 

```{r}
lang_books <- books %>%
  mutate(language_code = 
         recode(language_code,
         'en-CA' = 'eng',
         'en-GB' = 'eng',
         'en-US' = 'eng')) %>% 
 count(language_code) %>% 
  arrange(desc(n))
lang_books

#English ... Well.. not hard to guess 
```

TASK 6: I am going to treat all the 0 as NA in num_page,
and replace them with the mean? I will find the shortest book.
```{r}
NA_books <- books %>% 
  select(num_pages,title) %>% 
  mutate(num_pages = na_if(num_pages, 0)) %>% 
  mutate(num_pages, coalesce(num_pages, mean(num_pages, na.rm = TRUE))) %>% 
  slice_min(num_pages, n=3, with_ties = FALSE)

NA_books
#It gives me three book that only had 1 page.
#Well, I don't think it's correct.... But I don't know how to get ride of 
#those clearly wrong numbers that aren't 0. There will be stupidly short 
#books, so I don't want to loose that.... Oh well. 
```


TASK 7: I will call the books which have less than 100
short books, 
between 100 and 500, medium books 
over 500, long books. 
```{r}
books %>% 
  mutate(book_length = case_when(num_pages < 100 ~ "Short Book",
                                 num_pages < 500 ~ "Medium Book",
                                 TRUE ~ "Long Book"
                                 ),
         .after = num_pages)

```


TASK 8: It's non-sense here.
An author is rated now by my formula:
Score = average_rating * (rating_count/median_rating_count)

I will drop all the 0 for now
```{r}
books %>% 
  select(authors,average_rating, ratings_count) %>%
  mutate(ratings_count = na_if(ratings_count, 0)) %>%
  drop_na(ratings_count) %>% 
  group_by(authors) %>% 
  summarise(score = 
              average_rating*
              (ratings_count/median(ratings_count, na.rm = TRUE))) %>% 
  arrange(desc(score))
#George R.R. Martin has the highest score. 
```


TASK 9: I am going to compare books in eng and in spa 
umm, my rule is stupid again.
add up the mean of all the col
bigger one win.
```{r}
eng_spa_books <- books %>% 
  select(language_code,ratings_count,num_pages, average_rating) %>%
  filter(language_code == c("eng","spa")) %>% 
  mutate(across(where(is.numeric), ~na_if(.x, 0))) %>% 
  filter(if_all(where(is.numeric), ~!is.na(.x))) %>% 
  group_by(language_code) %>% 
  summarise(score = mean(ratings_count) 
            + mean(num_pages) 
            + mean(average_rating))
eng_spa_books
#eng is higher by a lot.... doesn't seem right.. 
```





