---
title: "R Notebook"
output: html_notebook
---
Data:
qb_revenue_breakdown
qb_monthly_sales
qb_competitors
qb_device_data
```{r}
library(tidyverse)
```
```{r}
revenue <- CodeClanData::qb_revenue_breakdown
sales <-CodeClanData::qb_monthly_sales
competitors <- CodeClanData::qb_competitors
device <- CodeClanData::qb_device_data
```

2 MVP
2.1 Part 1
Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
revenue %>% 
  ggplot(aes(x = Product, y = Revenue))+
  geom_col(aes(fill = Year)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = "Sources of revenue across 2018 and 2019\n")
```

Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).
```{r}
sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount, group = Cashflow),
            colour = "pink", size = 4)+
  labs(title = "Sale of KwikBit Unit 1\n")
```



Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}
sales %>% 
  filter(Cashflow == "Total Revenue") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount, group = Cashflow),
            colour = "lightblue", size = 4)+
  labs(title = "Cost of revenue\n")
```


Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
competitors %>% 
  ggplot(aes(x = Year,
             y = Revenue))+
  geom_area(aes(group = Company,
            fill = Company))+
  labs(title = "Sale of personal fitness tracker over last 5 years")
```

Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
competitors %>% 
  ggplot(aes(x = Year,
             y = Revenue))+
  geom_line(aes(group = Company,
            colour = Company),
            size = 2,
            alpha = 0.5)+
  geom_point(aes(colour = Company),
             size = 3)+
  labs(title = "Sale of personal fitness tracker over last 5 years",
       subtitle = "As line graph\n")
```


Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.
```{r}
device %>% 
  unite(time, c(hours, mins), sep = ".") %>% 
  mutate(time = as.numeric(time)) %>% 
  ggplot(aes(x= time, y = counts)) +
  geom_line(aes(group = id, colour = id))+
  facet_grid(id~device,scales = "free_y")+
  labs(title = "Compare of Steps Counts between Companies\n")
```



2.2 Part 2
Question 1.
Take the plots that you produced in part one and now polish them by:

Adding appropriate labels
Changing the scales and coordinates when appropriate.

Applying a unified theme, which is described below:
Graphs should have white backgrounds, and use colour .
There should be faint grid lines.
Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
All plots should use colours from the following company colour scheme.


```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

my_theme <- function() {
  theme( text = element_text(size = 12),
         panel.background = element_rect(fill = "white", colour = "grey"),
         panel.grid = element_line(colour = "grey",
                                         linetype = 2, 
                                        size = 0.1),
         title = element_text(size = 16),
         axis.text = element_text(size = 8),
         axis.title = element_text(size = 8)
  )
}

```




```{r}
#plot 1
revenue %>% 
  ggplot(aes(x = Product, y = Revenue))+
  geom_col(aes(fill = Year)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = "Sources of revenue across 2018 and 2019\n")+
  my_theme()+scale_fill_manual(values = col_scheme)
  
```


```{r}
sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount, group = Cashflow),
            colour = col_scheme[1], size = 4)+
  labs(title = "Sale of KwikBit Unit 1\n")+
  my_theme()
```





