---
title: "R Notebook"
output: html_notebook
---

playing with the dataset
```{r}
library(tidyverse)
library(shiny)
game <- CodeClanData::game_sales
```

```{r}
colnames(game)
```
```{r}
game %>% 
  select(genre) %>% 
  distinct() %>% 
  pull()
```

[1] "name"            "genre"           "year_of_release"
 [4] "publisher"       "sales"           "critic_score"   
 [7] "user_score"      "developer"       "rating"         
[10] "platform"

```{r}
game %>% 
  filter (genre == "Misc") %>% 
ggplot()+
  aes(x = user_score, y = critic_score)+
  geom_point(aes(colour = genre, size = sales), aplha = 0.5)+
  labs(title = "Public vs Critic")
```
```{r}
ggplot(game)+
  aes(x = platform, y = sales)+
  geom_col(fill = 'pink')
```
 [1] "Sports"       "Racing"       "Platform"     "Misc"         "Puzzle"      
 [6] "Simulation"   "Action"       "Shooter"      "Fighting"     "Adventure"   
[11] "Role-Playing" "Strategy"   

```{r}
game %>% 
  filter(genre %in% c("Sports","Racing","Platform","Misc","Puzzle" )) %>% 
  ggplot(aes(x = genre,  y = sales))+
  geom_boxplot(aes(colour = genre))+
  ylim(0,2)+
  geom_jitter(alpha = 0.3, aes(colour = genre))+
  labs(title = "Sales for each genre")
```
one game cross year sales 
```{r}

```

  column(2,
                 tags$img(src = 'nook.png',
                          height=100,width=80))
                          
                           fluidRow(plotOutput("score_output")),
          fluidRow( plotOutput("sale_output")),
          
          
          
          
          tabsetPanel(
    tabPanel("Sale", plotOutput("sale_output")),
    tabPanel("Score", plotOutput("score_output)))