---
title: "R Notebook"
output: html_notebook
---
1 MVP
Now we’ll go back to CI creation in the normal fashion. We’ll take the ames data from the CIs lab earlier today and regard it now as a sample, we won’t be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!



Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
library(tidyverse)
library(janitor)
library(infer)
ames <- read_csv("data/ames.csv") %>% clean_names()
```



Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ames %>% 
  ggplot(aes(lot_area))+
  geom_histogram(col = "white", fill = "lightblue")
#no not normal distribution, all data concentrated around small interval
```



Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.
```{r}
resample_lot_area <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")
resample_lot_area %>%
  visualise(bins = 30)
#it looks almost like a noraml distribution here 
```



Task 4.
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution
```{r}
infer_ci_95 <- resample_lot_area %>%
  get_ci(level = 0.95, type = "percentile")
# lower ci 9880.404
#upper_ci 10454.81

resample_lot_area %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95)
```



Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?
```{r}
infer_ci_99 <- resample_lot_area %>%
  get_ci(level = 0.99, type = "percentile")
# lower ci 9809.478
#upper_ci 10571.19
#it's a wider range and makes perfect sense
resample_lot_area %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99)
```



Task 6.
Calculate the point estimate of the mean(lot_area)
```{r}
mean_lot_area <- resample_lot_area %>%
  ungroup() %>%
  summarise(mean_lot_area = mean(stat)) 

mean_lot_area
#10148.43
#i don't think that i understood here?? 
#point estimate is just a way to refer to
#the mean of lot_area of this sample in this case? 
```

