---
title: "R Notebook"
output: html_notebook
---
Homework 

Question 1.

Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc.?
```{r}
library(tidyverse)
library(CodeClanData)
drinks_content
#this line  above already had dimensions.
dim(drinks_content)
names(drinks_content)
summary(drinks_content)
str(drinks_content)
glimpse(drinks_content)
head(drinks_content)
#all the lines above is just to check things... 
```



Question 2.

Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.
```{r}
calories <- select(drinks_content, Beverage_category, Beverage, Beverage_prep, Calories)
is.na(calories)
#this line above returns a lot of False, it works but probably not the best way.
```
```{r}
?drop_na()
```
the answer did a filter is.na then count the na using summarise


Question 3.

Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract 135 from the calories to see which drink have more or less than 10 cups of sugar).

Question 4.

Summarise the mean number of calories in each beverage_category. Which 3 category of drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.

```{r}
calories %>% 
  mutate(calorie_diff = Calories - 135)%>%
  drop_na() %>% 
  group_by(Beverage_category) %>% 
  summarise(average_cal = mean(Calories, na.rm = TRUE)) %>% 
  arrange(average_cal)

```
The answer did arrange then head (3) for most and least 

This is part of Question 4:
My summary, coffee, shaken iced beverages and classic espresso drinks 
have the least calories.
Signature espresso drinks, frappuccion blended coffee and smoothies 
have the highest calories.







Question 5.

Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?
```{r}
bev_repgp<- calories %>% 
  group_by(Beverage_prep) %>% 
  summarise(average_bev = mean(Calories, na.rm = TRUE)) %>% 
  arrange(average_bev)
bev_repgp
```



Question 6.

Which Beverage_prep type contains more than the average calories of all drinks?
```{r}
average_all <- calories %>%
  select(Calories) %>% 
  summarise(mean(Calories))
  #I will not call it as  I can see from the environment.
  
  #Now I got average  of all drinks 
```

```{r}
bev_repgp %>% 
  filter(average_bev > average_all)

#Why is the average_all is not a value?
```



Question 7.

Which is the best type of coffee drink (and by ‘drink’ we mean the combination of Beverage_category, Beverage and Beverage_prep) to get if you’re worried about consuming too many calories?

```{r}
calories %>% 
  group_by(Beverage_category) %>%
  group_by(Beverage) %>% 
  group_by(Beverage_prep) %>% 
  arrange(Calories)
#Answer: Taxo Tea Drinks - Tazo Tea  - Short ? Not sure about this. 
```


