---
title: "R Notebook"
output: html_notebook
---

Calculate the  and  to settle this dispute.
create a crew column containing values TRUE or FALSE to help with this
For prob(survived∣crew) think ‘what proportion of the crew survived?’, and similar for prob(survived∣passenger)
You may want to use prob and gtools later in the homework
```{r}
library(tidyverse)
library(gtools)
titanic <- read_csv('data/titanic.csv')
source('prob.R')
```
have a look at the data
```{r}
titanic %>% 
  distinct(survived)
```
```{r}
titanic_s <- titanic %>% 
  select(class, survived) %>% 
  mutate(is_passenger = case_when(class %in% c('3rd','2nd','1st') ~ TRUE,
                           TRUE ~ FALSE)) %>% 
  mutate(survived = case_when(survived == 'no' ~ FALSE,
                              TRUE ~ TRUE))
titanic_s
```
```{r}
library(janitor)
titanic_s %>% 
   tabyl(survived, is_passenger) %>% 
  adorn_percentages(denominator = 'all') %>% 
  adorn_title()
#for me to check my answers 

crew_percent <- titanic_s %>% 
  filter(!is_passenger) %>% 
  summarise(n()/nrow(titanic_s))

pass_precent <- 1 - pass_percent

survived_percent <- titanic_s %>% 
  filter(survived) %>% 
  summarise(n()/nrow(titanic_s))

not_survived_percent <- 1 - survived_percent

crew_percent #0.40326
pass_precent #0.59673
survived_percent # 0.3221
not_survived_percent #0.6778
```


prob(survived∣crew) from above maths prob = 0.0956/0.40326 = 0.237

```{r}
titanic_s %>% 
  filter(!is_passenger) %>% 
  summarise(prob = mean(survived))
```


prob(survived∣passenger)  by maths prob = 0.22655/0.59673 = 0.379
```{r}
titanic_s %>% 
  filter(is_passenger) %>% 
  summarise(prob = mean(survived))
```
passenger is more likely to survive 

--------------------------------------------

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```
P(a < 5) = 4/6 = 2/3
```


Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?
```
6*6*6*6= 1296
```


Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
```{r}
four_dice <- rolldie(4)

num_5_6_7 <- four_dice %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total %in% c(5,6,7)) %>% 
  summarise(num = n())

#34 outcomes 
```

what is the probability of this event?
```{r}
four_dice %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total %in% c(5,6,7)) %>% 
  summarise(prob = n()/nrow(four_dice))

#0.0262
```
what assumptions do we apply in answering part ii?

_the event_ means roll a total of 5 OR 6 OR 7


Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
```{r}
1/5 * 1/4 * 1/3 *1/2 = 1/120
```


Question 5.
I roll _six dice_:
what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
```
1/6 ^6 = 1/46656
```
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
```
(1/46656)/(6!)= 0.0154
```

Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?
```
(1/8) / (1/2) = 1/4
```

