---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyr)
library(tidyverse)
```

Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
tweets <- read_csv("data/code_clan_tweets.csv")
dim(tweets)
names(tweets)
```


Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).
```{r}
favourites <- tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(count = sum(favorite_count))
```



Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
mean <- tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean_retweet = mean(retweet_count))
#split? My understanding is that it means  grouped. 
```


Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
likes <- tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_likes = sum(favorite_count)) %>% 
  arrange(desc(total_likes))
  
```


Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).
```{r}
text <- tweets %>% 
  select(text, display_text_width)

text %>% summarise(char = sum(nchar(text)))

text %>% 
  summarise(char2 = sum(display_text_width))

#not the same..?? 
```

Here's the answer. 
```
codeclan_tweets %>%
  summarise(avg_tweet_length = mean(display_text_width))
  
code_clan_tweets_text <- codeclan_tweets %>%
  mutate(count_str_length = str_length(text)) %>%
  select(count_str_length, display_text_width)

code_clan_tweets_text
```

Question 6.
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
info <- read_csv("data/code_clan_info.csv")

sta <- info %>% 
  select(status_url, tweet_id)

joined <- full_join(tweets, sta, by = "tweet_id")

```


Question 7.
From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.
```{r}
codeclan_hashtags <- joined %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  filter(!is.na(hashtags))

```


Question 8.
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(.
Hint
Try a regex pattern "c\\(". The double backslash is necessary in R to mark a backslash as itself being escaped.
```{r}
str_hash <- codeclan_hashtags %>%
  select(hashtags) %>% 
  pull() %>% 
  str_sub(start = 1, end = 2) %>% 
  str_detect("c\\(")
```
That's not what the question asked, here's the answer 
```
hashtags_multiple <- codeclan_hashtags %>% 
  mutate(first_letters = str_sub(lowcase_hashtag, 1, 2)) %>%
  filter(str_detect(first_letters, "c\\("))
```

Question 9.
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.
Hint
You may need to make sure your tweets are all the same case before searching.

```{r}
tweets  %>% select(text) %>% 
  mutate(text = str_to_title(text)) %>% 
  mutate(edin_count = str_detect(text, "Edinburgh")) %>% 
  summarise(sum(edin_count))
  
```

Question 10.
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.
Hint
Think about all the different characters which could be in a Twitter username, do a bit of online research
```{r}
tweet_users <- tweets %>% select(text)
pa <- "@[A-Za-z0-9_]+"

str_extract_all(tweet_users, pa )
```

