---
title: "R Notebook"
output: html_notebook
---
2 MVP


Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.
```{r}
library(tidyverse)
backpack <- CodeClanData::backpack
colnames(backpack)
dim(backpack)
```

Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.
```{r}
ggplot(backpack)+
  aes(x = backpack_weight)+
  geom_bar(fill = "seagreen")+
  labs(x = "Backpack Weight",
       y = "Count",
       title = "Distribution of Backpack Weight")+
  scale_y_continuous(breaks = (0:12))

#The graph shows a rough normal distribution with the center around 10. 
#Towards the higher end there are some gaps in the graph
```

Question 3.

Are there differences in backpack weight between sex?
```{r}
ggplot(backpack)+
  aes(x = backpack_weight)+
  geom_bar(aes(fill = sex))+
  facet_grid(~sex)+
  labs(x = "Backpack Weight",
       y = "Count",
       title = "Distribution of Backpack Weight\n")+
  scale_y_continuous(breaks = (0:12))
#Female has a higher backpack weight on average. 
```

Question 4.

What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack)+
  aes(x = body_weight, y = backpack_weight)+
  geom_point(colour = "blue")+
  geom_smooth()+
  labs(y = "Backpack Weight",
       x = "Body Weight",
       title = "Backpack Weight vs Body Weight")

#Doesn't seem to have a clear corelation 
  
```


Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
```{r}
ggplot(backpack)+
  aes(x = body_weight, y = backpack_weight)+
  geom_point(aes(colour = sex))+
  facet_wrap(~sex, scales ="free")+
  geom_smooth()+
  labs(y = "Backpack Weight",
       x = "Body Weight",
       title = "Backpack Weight vs Body Weight",
       subtitle = "Compareing between men and women")
#No corelation still 
```

Question 6.

What proportion of students report back pain?
```{r}
backpack_p <- backpack %>% 
  mutate(back_problems = ifelse(back_problems == 1,"Back Pain", "No Back Pain"))

ggplot(backpack_p)+
  aes(y = back_problems, x = "",fill = back_problems)+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start = 0) + 
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "",
       y = "",
       title = "Back problems among students\n",
       fill = "Back Problems")

  #Most students don't have back problems but it's till a high percentage 
```

Question 7.

Is this proportion different between men and women?
```{r}
ggplot(backpack_p)+
 aes(x=sex, fill=back_problems) +
 geom_bar(position = "fill") +
 facet_grid(~sex)+
 coord_polar("y", start = 0)+
 theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
       axis.ticks.y = element_blank(),
        axis.text.y = element_blank())+
  labs(x = "",
       y = "",
       title = "Back problems among students",
       subtitle = "Male vs female\n",
       fill = "Back Problems",)
#Higher percentage female experience back pain, it's a lot higher than male. 
```

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.
```{r}
ggplot(backpack_p)+
  aes(x=backpack_weight, y=body_weight)+
  geom_point(aes(shape = back_problems, colour = sex))+
  facet_grid(back_problems~sex)+
  geom_smooth()+
  labs(x = "Backpack weight",
       y = "Body weight",
       title = "Body weight/Backpack weight relationsip with back problems")
#there is not clear correlation between body weight and backpack weight
#only few male experiecen back pain
```
```{r}
ggplot(backpack_p)+
  aes(x=back_problems, y = ratio, fill=back_problems) +
  geom_boxplot() + 
  geom_jitter(width=0.1,alpha=0.2) +
  labs(x = "Back Problems",
       y = "Ratio",
       title = "Ratio vs Back Problems")
#people have back pain has a higher mean ratio 
```
```{r}
ggplot(backpack_p)+
  aes(x=back_problems, y = ratio, fill=back_problems) +
  geom_boxplot() + 
  geom_jitter(width=0.1,alpha=0.2) +
  facet_grid(~sex)+
  labs(x = "Back Problems",
       y = "Ratio",
       title = "Ratio vs Back Problems",
       subtitle = "for both female and male")
#people have back pain has a higher mean ratio 
#male has slight lower ratio and lower percentage of back pain 
```





3 Extensions


Question 1.

Does reported backpain differ across the year groups? Ignore year 0 in your data.
```{r}
backpack_p %>% 
  filter(year != 0) %>% 
  ggplot(aes(x=year))+
  geom_bar(aes(fill = back_problems),position = "fill") +
  labs(x = "Years",
       y = "Percentage",
       title = "Back pain across years\n",
       fill = "Back pain")+
  scale_x_continuous(breaks = (1:6))
#year 3 has the highest percentage of backpain reports
#year6 has no backpain reported. 
```


Question 2.

Is there a difference between how heavy the bags those in different years carry?
```{r}
backpack_mean <- backpack %>% 
  group_by(year) %>% 
  summarise(mean = mean(backpack_weight)) %>% 
  filter(year != 0)


ggplot(backpack_mean)+
  aes(x = year, y = mean)+
  geom_line(colour = "pink", size = 2)+
  geom_point(colour = "red4", size = 3)+
  scale_x_continuous(breaks = (1:6))+
  labs(x = "Year",
       y = "Mean backpack weight",
       title = "Backpack weight across all years\n")
#the graph shows a clear increase from year 1 to 5 and a sharp drop at year 6
#The data from year 6 is not a lot, this could be why
#it also explains why year 6 has no backpain reports 
```

