---
title: "R Notebook"
output: html_notebook
---
2 MVP

2.1 Question 1
We are going to use a dataset on house sales in Ames, Iowa over a number of years. We will be interested in the SalePrice of houses (though we should clean_names() the data, so this will end up as sale_price). Load the data and explore it.

```{r}
library(tidyverse)
library(janitor)
library(infer)
ames <- read_csv("data/ames.csv") %>% clean_names()
sale_ames <- ames %>% 
  select(sale_price)
```


2.2 Question 2
Plot a histogram of sale_price. Is the distribution normal?

```{r}
sale_ames %>% ggplot(aes(sale_price))+
  geom_histogram(col = "white", fill = "lightblue")
#does look like normal distribution
```


2.3 Question 3
Calculate the population parameter mean of sale_price. Store it in a variable, as we’ll need this value later when we check if each CI contains the parameter value or not.
```{r}
sale_price_mean <- sale_ames %>% 
  summarise(mean_price = mean(sale_price))

sale_price_mean
  
```



2.4 Question 4
Now we are going to: - take 1000 random samples each of size 100 from sale_price in ames - create a boostrap sampling distribution of mean(sale_price) from each 100-observation sample (use 1000 reps) - calculate the 95% CI for each bootstrap distribution - store the upper and lower bounds of the CI in a tibble called results

Use the infer workflow to generate the bootstrap distributions and CIs. This code will be pretty hard to write. Think about wrapping the sample creation and infer code in a for loop to generate 1000 random samples and CIs. Create an empty results tibble before the loop, and bind_rows() to it every time you generate a new set of CI bounds.
```{r}
list = c()
for (i in 1:1000){
resample_sale <- sale_ames %>%
  rep_sample_n(size = 100, replace = TRUE, reps = 1000) %>%
  summarise(mean = mean(sale_price),
       lower_bound = quantile(mean, probs = 0.025),
       upper_bound = quantile(mean, probs = 0.975)
  )
  list[[length(list) + 1]] <- resample_sale
  return(list)
}
list
```




2.5 Question 5
Pipe results to mutate() to add a new variable popn_param_in_ci which will be TRUE if the population parameter we calculated earlier is between lower and upper, and FALSE otherwise.

[Hint if you stored your parameter in a tibble earlier (e.g. as the result of a summarise() pipe), extract it here as a numeric before you compare with upper and lower]
```{r}
list %>% 
  mutate(popn_param_in_ci = case_when(lower_bound < 180796.1	& upper_bound > 180796.1	~ TRUE,
                               TRUE ~ FALSE))
```


2.6 Question 6
Perform an appropriate summarise() to determine the proportion of CIs that contain the population parameter. Our confidence level was 95% (equivalent to a proportion of 0.95). Is your proportion close to that value?



2.7 Question 7
Have a think about what all this means, make a list of any points you don’t understand. - Imagine you had only a single 100-observation sample of the ames data (say from a 100 house survey). - Would you know ahead of time whether the CI for mean(sale_price) from your particular sample contains the correct population parameter or not?


